Towards a Wide-Coverage Grammar for Swedish Using GF

### 2012-01-02 doc/report/report.tex
report: fix comments

\begin{document}
% ska gå att förstå och locka till läsning
%ska tydligt beskriva vad rapporten handlar om
%ska innehålla vettiga sökord
\title{Towards a wide-coverage grammar for Swedish using GF} %A nice titleScaling up a GF grammar and preparing it for cool stuff for Swedish}
\author{Malin Ahlberg}
\maketitle
\newpage

@@

\section{Grammatical Framework}
\label{sec:gf}
The main component of the project is the Grammatical Framework (GF) \cite{gfbok}, %It is
a grammar formalism based on Martin-Löf type theory \cite{martinlof}. GF is
designed for multilingual applications and represents a formalism
%equivalent to Parallel Multiple Context-Free Grammars (Seki \& al. 1991), an instance of
%generalized context free grammar (GCFG) it is hence
stronger than mildly context-free grammars. The framework has  hence the same expressiveness
as Tree Adjoining Grammars \cite{tag} and Head Grammars \cite{hg}.

>>>>

\begin{document}
% ska gå att förstå och locka till läsning
%ska tydligt beskriva vad rapporten handlar om
%ska innehålla vettiga sökord
\title{Towards a Wide-Coverage Grammar for Swedish Using GF} %A nice titleScaling up a GF grammar and preparing it for cool stuff for Swedish}
\author{Malin Ahlberg}
\maketitle
\newpage

@@

\section{Grammatical Framework}
\label{sec:gf}
The main component of the project is the Grammatical Framework (GF) \cite{gfbok}, %It is
a grammar formalism based on Martin-Löf type theory \cite{martinlof}. GF is
designed for multilingual applications and represents a formalism
%equivalent to Parallel Multiple Context-Free Grammars (Seki \& al. 1991), an instance of
%generalized context free grammar (GCFG) it is hence
stronger than mildly context-free grammars. 
The framework's %has hence the same
expressiveness is hence stronger than 
Tree Adjoining Grammars \cite{tag} and Head Grammars \cite{hg}, and shown
equivalent to Parallel Multiple Context-Free Grammar \cite{pmcfg} by \cite{peter}.
